Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-04 paper/sections/metis-language-and-proofs.tex
[ paper ] improved proof rules descriptions.

\textit{Normalization.}
Each application of the clausify rule described above is preceded by
\canonicalize rule. Both rules aim to perform a common task for
automatic theorem provers, clausification, mainly described on paper
by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.

\Metis uses the \canonicalize rule to
normalize a propositional formula that comes from an axiom or a
definition. It often converts each expression in one of its normal
form: the conjunctive normal form, the negative normal form or the
disjunctive normal form. Next, this rule simplifies the formula
with some definitions, applying recursively on the structure's
formula conjunctions and disjunctions simplifications to remove
tautologies (see Fig.~\ref{fig:conjunctive-disjunctive-simpl} for a
list of these theorems. We assume the commutative property for the
conjunction and disjunction connectives).
We refer the reader to see Section~\ref{sssec:normalization} for the
lemmas and theorems described there.

>>>>

\textit{Normalization.} We observed \clausify rule described above is preceded by \canonicalize rule when \Metis introduces at some point of the derivation an axiom or a definition of the problem. In that case, both rules aim to perform a common task for
automatic theorem provers, Clausification, mainly described on paper
by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. When the
aforementioned case does not occur we argue \canonicalize transforms
proposition into another one that mainly matches with its negative
normal form, its conjunctive normal form or its disjunctive normal
form. In addition, \canonicalize could also perform other tasks like
removing logic constants (⊥, ⊤), definitions, and tautologies, or even reorder both conjunctions and disjunctions of the proposition.

For instance, assuming the commutative properties for both
connectives, conjunction and disjunction, and using the theorems
in Fig.~\ref{fig:conjunctive-disjunctive-simpl}, \canonicalize could
use them to reduce a proposition to a one smaller by applying
recursively on the structure of the formula those theorems.
We refer the reader to see Section~\ref{sssec:normalization} to continue our approach to emulate this rule.
